

%\documentclass[a4paper,twoside]{report}
\documentclass[a4paper, 11pt]{book}

\usepackage[small,bf]{caption}

% for images
\usepackage{graphicx}
\usepackage{subfig}

% to skip space but not indent for paragraph
\usepackage{parskip}

% for jumping to correct location from editor
%\usepackage{pdfsync}

% for UTF-8 support
\usepackage[utf8]{inputenc}

% for sideway tables
%\usepackage{rotating}

% for math
\usepackage{amsmath}

% for image wrapping
%\usepackage{wrapfig}

% for algorithms
\usepackage{algorithm}
\usepackage{algorithmic}

% for nice sitation references
\usepackage{natbib}

% for fancy headers
%\usepackage{fancyhdr}
%\setlength{\headheight}{15.2pt}
%\pagestyle{fancy}

% for internal references, USE AS LAST
\usepackage[colorlinks]{hyperref}




% for better image placing
%\renewcommand{\topfraction}{0.85}
%\renewcommand{\textfraction}{0.1}
%\renewcommand{\floatpagefraction}{0.75}


\begin{document}

% Titel pagina
\pagenumbering{Alph}
\thispagestyle{empty}

\title{Sonic Gesture}
\author{G. J. Molenaaar}
\date{2010}
\maketitle{}

\chapter*{Abstract}
A real\-time method for estimating hand poses in video using a normal RGB camera. The method uses a probabilistic skin color histogram model for pixel based limb localization and HOG features for classification. The performance of HOG is compared with SURF where HOG yielded superior performance. As classifiers k-NN and SVM with the RBF and $\chi^2$ kernels are evaluated, where SVM in combination with the $x^2$ kernel performed best. All evaluation is done with a new constructed dataset consisting of 72 recordings of 20 people performing 28 hand symbols based upon the Curwen Solfege method. A prototype mapping the hand poses into sound is described, this to demonstrate the practical usability of the method in a real-time situation.

% contents etc
\pagenumbering{Roman}
\setcounter{page}{1}

\tableofcontents{}
\listoffigures{}
\listoftables{}

\chapter*{Acknowledgements}
Until not so long ago I never dared dreaming to do this; writing the acknowledgments of my Master Thesis. I'm really proud I came this far and I'm really content with the subject and results of my research.

\cleardoublepage
\pagenumbering{arabic}
\setcounter{page}{1}

\include{intro}

\include{bodyparts}

\include{gestures}

\include{experiments}

\include{sonicgesture}

\include{conc}


\cleardoublepage
\phantomsection
\addcontentsline{toc}{chapter}{Bibliography}
\bibliography{thesis}
\bibliographystyle{plainnat}


\include{appendix}



\end{document}

