\chapter{Technical Introduction}
\label{ch:techintro}

\section{Input: The hand poses}

\section{Color space conversion}
Hue, Saturation and Intensity. Only hue and Saturation is used to make lightning intensity independent.

\section{Face detection - Haar classifier}
The hand pose chain stats with detecting a face in the first video frame. This is done using the haar classifier, a  boosted rejection cascade that is trained with Haar-like wavelet features\cite{Lienhart02anextended}.
Haar wavelets, histogram building.

\section{Skin color histogram}
When a face is found a color model for the subjects skin can be created. this is done by constructing a 2 dimensional histogram with the Hue and Saturation values. The optimal number of bins can't be exactly determined, a not to high or not to low value is important. 
Sonic Gesture used 180 bins for Hue and 256 for Saturation. \marginpar{EXPERIMENT WITH THIS}

\section{Blob detection}
Back projection, morphological transformations

\section{Pixel grouping, contour extraction}
join touching pixels

\section{Blob labeling}
Heuristics for blob labeling

\section{Blob label stabilization}
Kalman filter (prediction) and template search

\section{Segmentation - removing background}

\section{Feature extraction}
calculate Histogram of Oriented gradients\cite{watanabe2009}

\section{Classifier}
KNN, maybe other classifiers? PCA?

\section{The stabalizer}
Thresholding histogram based stabalizer, maybe done before (better)?

\section{Training phase}
recording video, manual labeling, extracting HOG features, trainig classifier

\section{Testing/performance/run phase}


\section{Output: Open Sound Control}
Open Sound Control (OSC), protocol for fast sound data transfer

\section{Implementation}
OpenCV, QT, CMake, Liblo, open source, website, maybe not required/important?
